Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-01 PAPER.tex
added cites

Determining the source of detections at higher $k$'s is more difficult. In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}). In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.

@@

This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}. In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e. data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).  It is in this last region that we search for the point at which an injected signal would be clearly detected.

One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data. Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.  This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself. In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual. We note that a high SNR detection will require a different method, but we show this one to... \cc{fill in..} \dcj{but we show this one to what?  Why not just leave it with a period}

>>>>

Determining the source of detections at higher $k$'s is more difficult. In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}). In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.

@@

This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}. In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e. data only). \cc{this next sentence does not make sense} As $P_{\rm in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself. Above some level the injected signal is clearly detectable.

One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data. Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.  This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself. In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual. We note that a high SNR detection will require a different method, but we show this one to... \cc{fill in..}
